\bf Promoting analysis reproducibility with accessibility: An example in evolutionary biology

### 2022-02-04 jsdse/Manuscript.tex
adding references

Primary documentation focuses on demonstrating usage function with examples that
work seamlessly, without errors. We argue that the opposite is needed to support
user adoption of reproducible workflows: demonstrate examples that do not work
as expected and exemplify ways to address them (Figure \ref{fig:first}).
We identify inputs that would give
a wide range of warnings and errors, focusing on demonstrating these cases. This
helps users to not be afraid of errors and warnings, but instead to use them to
their advantage.
We also identify effects of warnings and errors downstream of the workflow.

>>>>

A practice that has become more and more widespread in programming languages pedagogical practices
is the use of typos and mistakes to normalize them for learners and show them how
to solve them when they are outside the classroom (\cite{shannon2015live}).
Yet, this is rarely done for written pedagogical materials.
Primary documentation focuses on demonstrating usage function with examples that
work seamlessly, without errors. We argue that the opposite is needed to support
adoption of reproducible workflows and support long term independence in learners
(\cite{gaspar2007restoring}).
We demonstrate examples that do not work
as expected and exemplify ways to address them (Figure \ref{fig:first}).

We identify inputs that would give
a wide range of warnings and errors, focusing on demonstrating these cases. This
helps users to not be afraid of errors and warnings, but instead to use them to
their advantage.
We also identify effects of warnings and errors downstream of the workflow.
